Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-01-14 Manuscript/HI_Model_ms.Rmd
updated manuscript files

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@keenan_terrestrial_2018; @friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Defined as conservation and land management efforts aimed at enhancing ecosystem carbon storage [@griscom_natural_2017], natural climate solutions are appealing because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. A growing number of sub-national jurisdictions have incorporated  as part of a suite of emissions reduction efforts to achieve carbon neutrality. However, effective implementation is complicated by the uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale.

Interannual fluctuations in carbon uptake by land ecosystems is the primary driver of year-to-year variation in atmosphereric CO~2~ growth rate
Interannual variability in climate, land use, and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017].

@@

The main Hawaiian Islands are a complex mosaic of natural and human-dominated landscapes overlain by steep climate gradients across relatively short distances.

>>>>

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@keenan_terrestrial_2018; @friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Defined as conservation and land management efforts aimed at enhancing ecosystem carbon storage [@griscom_natural_2017], natural climate solutions are appealing because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. However, effective implementation is complicated by the uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale. Despite this uncertainty, evidence indicates that variability in carbon uptake by land ecosystems, both year-to-year and over the long term, is primarily driven by fluctuations in climate, land use, and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017; @friedlingstein_global_2019]. Spatially explicit future projections of ecosystem carbon balance incorporating the interactive effects of land use and climate could therefore provide a reference point to evaluate the effectiveness of land-based mitigation. Although a complex challenge, the growing number of sub-national jurisdictions that plan to incorporate land-based mitigation strategies into their emissions reduction efforts would benefit from understanding how future climate-biosphere feedbacks will affect ecosystem carbon balance in their respective regions [@sleeter_effects_2019].

The State of Hawai`i exemplifies the challenges and complexity of projecting the interactive effects of climate and land use change on ecosystem carbon balance. The main Hawaiian Islands are a complex mosaic of natural and human-dominated landscapes overlain by steep climate gradients across relatively short distances. Mean annual temperature ranges from ~4 - 24° C [@giambelluca_evapotranspiration_2014] and mean annual rainfall ranges from ~180 - 9500 mm [@giambelluca_online_2013], with minimal seasonal variation in climate. Ecosystem carbon stocks across the Hawaiian Islands are still strongly influenced by the legacy of past land-use change [@asner_high-resolution_2011]. Thousands of hectares of land were deforested beginning in the late 19th century to make way for sugar plantations and cattle pasture [@cuddihy_alteration_1990]. Beginning in the latter half of the 20th century, this agricultural land has since been steadily converted to urban areas, commercial forestry plantations, or simply abandoned and colonized by non-native grass species [@suryanata_diversified_2009; @perroy_evolving_2016].

@@

We used a fully coupled consider four unique future scenarios
